Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-09 paper/main.tex

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
\usepackage[backend=biber]{biblatex}
\addbibresource{main.bib}

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Beijing, China \\
1561010}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

this is the explaination  \cite{BARA2020106658}

@@

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/dataprocess.png}}
    \caption{Data processing}
    \label{fig4}
\end{figure}

>>>>

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx} 
\usepackage{textcomp}
\usepackage{xcolor} 
\usepackage[backend=biber]{biblatex}
\addbibresource{main.bib}
\newcommand{\subparagraph}{}

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Beijing, China \\
1561010}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Guizhou, China \\
benji.tong1117@gmail.com}
\and
\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

\subsubsection{Overview}
World Bank Light Every Night is a comprehensive data repository of light satellite images collected at night by 
two sensors for the past 30 years: National Defense Meteorological Satellite Program (DMSP) Line of Business Scanning 
System (OLS), data from 1992 to 2017.Visible infrared imaging radiometer suite (VIIRS) day and night band (DNB) data are 2012-2020.

Both DMSP-OLS and VIIRS-DNB sensors capture various low-light emission sources from the earth as optical data. These light source 
data mainly include brightness data generated by various human activities, such as city lights, gas flares, fishing boats, and 
agricultural fires, and also capture other natural light phenomena at night, such as aurora. The data repository is released and 
can be used for analysis. The data repository was established by the World Bank in cooperation with the National Oceanic and Atmospheric 
Administration (NOAA) and the University of Michigan. Most of the basic data come from the NOAA National Environmental Information 
Center ( NCEI) file.

After continuous exploration, development, updates, and upgrades, the University of Michigan’s additional processing supports access 
in cloud-optimized GeoTIFF format (COG) and searches using Spatio-temporal Asset Catalog (STAC) standards. The ever-improving standards 
facilitate the analysis and become part of the ready data ecosystem, which is improving access to geospatial data sets, which makes it 
more widely accepted by the public and can be easily discovered, processed, and analyzed Geospatial data. Our project data will also use 
cloud-optimized GeoTIFF format (COG) and STAC standards to implement network-level applications.

\subsubsection{Remote sensing}
Research by NASA shows that modern remote sensing technology began with the invention of the camera more than 150 years ago. The 
first original photo appeared as a "still image", but it inspired people's ideas and practices for shooting and looking down on 
the surface of the earth. This idea appeared in the 1840s. The first photos were used for topographic mapping. Later in the First 
World War, the cameras mounted on the aircraft provided a bird's-eye view of a considerable surface area and provided a large amount 
of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached 
a qualitative leap. It is now commonly used to describe the science and art of identifying, observing, and measuring objects without 
directly touching them. The process involves detecting and measuring radiation of different wavelengths reflected or emitted from distant 
objects or materials, through which they can be identified and classified by category/type, substance, and spatial distribution (NASA,2021, August 28).

\paragraph{Orbits}

\subparagraph{Polar and non-polar}

Polar-orbiting satellites(Fig.~\ref{satellites})are located in an orbital plane that is nearly 90 degrees inclined to the equatorial 
plane. This tilt allows the satellite to perceive the entire earth, including polar regions, to observe locations that are difficult 
to reach from the ground. Many polar-orbiting satellites are considered sun-synchronous, which means that the satellite passes through 
the same position at the same solar time in each cycle. The polar orbit can be ascending or descending. In an ascending orbit, the satellite 
moves from south to north as it passes the equator. In descending orbit, the satellite moves from north to south.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/1.1.1.png}}
    \caption{Polar-orbiting satellites}
    \label{satellites}
\end{figure}

\subparagraph{Low-Earth orbit}

Low Earth Orbit (LEO) is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
surface of the earth (NASA,2021, August 28).It is the most commonly used orbit for satellite imaging because it is possible to take 
higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
orbits the earth about 16 times a day (ESA, n.d.).

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/1.1.2.png}}
    \caption{Low Earth Orbit }
    \label{LEO}
\end{figure}

\subparagraph{Geostationary}

The orbit of a geostationary satellite can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can 
be fixed at one longitude of the equator. There are hundreds of communication satellites and several weather satellites in such orbits.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/1.1.3.png}}
    \caption{Geostationary}
    \label{Geostationary}
\end{figure}

\subparagraph{Electromagnetic Spectrum}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/1.2.png}}
    \caption{Electromagnetic Spectrum}
    \label{Spectrum}
\end{figure}

\subparagraph{Radio}

Very Low Frequency (VLF):ELF is extremely low frequency and extremely low frequency, and its frequency is in the range of 
300 Hz to 30 kHz. It is a kind of radio wave, just like AM/FM signal, but with a lower frequency. It is very useful because 
it is mainly reflected at a height of 60-90 kilometers in the D zone of the earth's ionosphere, so it is effectively guided 
to a global distance in the earth's ionospheric waveguide. It is widely used to set up radio receivers almost anywhere on 
the earth. This signal can receive short radiation from lightning strikes in half of the earth (Stanford VLF Group. n.d.).

Low Frequency (LF):Low frequency refers to the radio frequency (RF) in the range of 30 kHz–300 kHz. Low\-frequency AM 
broadcasting services are widely used in Northern Europe, North Africa, and Asia. In the current era, its main uses are 
aircraft beacons, navigation (LORAN), information, and weather systems. Numerous time signal stations such as MSF, DCF77, 
JJY, and WWVB are located in this frequency band, which is also called the kilometer band or kilometer wave (Low\_frequency,n.d).

Medium Frequency (MF)\:Medium Frequency means radio frequency (RF) in the range of 300 kHz to 3000 kHz. For example, 
the AM broadcast band is a medium wave (MW), and the MF band is also called the 100-meter band, which ranges from 100 
to 1000 hundred meters (Medium\_frequency,n.d).

High Frequency (HF):The wave frequency of the high-frequency electromagnetic field is between 300 MHz and 3 GHz, and the 
wavelength is from 1 m to 10 cm. It is mainly human-generated non-ionizing electromagnetic radiation, which does not occur 
naturally in the environment, excluding low-amplitude VHF (Very high frequency) cosmic radiation. With the rapid development 
of wireless technology, HF is increasingly appearing in the environment.

\subparagraph{Microwave}

Very high frequency (VHF) is ITU's electromagnetic wave in the range of 30 to 300 megahertz (MHz), and the corresponding 
wavelength is ten meters to one meter (Wikimedia Foundation. (2021, August 14).

Ultra-high frequency (UHF) is the ITU's 300 megahertz (MHz) and 3 gigahertz (GHz), also known as the decimeter band because 
the wavelength ranges from one meter to one-tenth of a meter. UHF radio waves propagate mainly through the line of sight; 
they can be blocked by various objects, and their transmission capacity will be limited by the blocking of objects. For example, 
TV broadcasting, mobile phones, GPS, WIFI, and walkie-talkies all use UHF to realize the dissemination and communication of data 
information (Wikimedia Foundation. (2021, August 8).

Super High Frequency (SHF):The Super High Frequency (SHF) range is ITU to 3 to 30 gigahertz (GHz). This frequency belongs to 
the microwave band, so radio waves with these frequencies are called microwaves. There are many devices in this frequency range, 
such as radar transmitters, wireless local area networks, satellite communications, and it is also used in industrial microwave 
heating, medical diathermy, and microwave hyperthermia to treat cancer (Wikimedia Foundation,2021, July 15).

Extremely high frequency (EHF) is a radio frequency in the electromagnetic spectrum from 30 to 300 gigahertz (GHz). Its frequency 
is between the ultra-high frequency band and the far-infrared frequency band, and below it is the terahertz frequency band. The 
wavelength of radio waves in this band varies from ten to one millimeter, so it is also called the millimeter-wave band and the 
radiation in its waveband is called millimeter waves (Wikimedia Foundation,2021, August 1).

\subparagraph{Infrared}

 Infrared radiation (IR) is a kind of radiant energy and electromagnetic radiation, which is invisible to humans, but we can 
 still feel it. It occurs when atoms absorb and release energy with frequent fluctuations. All objects in the universe emit a 
 certain degree of infrared radiation, such as the sun, fire, and the emergence of thermal imaging technologies are the research 
 results of infrared technology (Lucas, J, 2019, February 27).

\subparagraph{Visible}

 The visible light spectrum is the segment of the electromagnetic spectrum that the human eye can view. Its wavelengths are 
 380 to 700 nanometers.The full spectrum of visible light can be divided into rainbow colors because each color has a different 
 wavelength. Violet has the shortest wavelength, about 380 nanometers, and red has the longest wavelength, about 700 nanometers 
 (NASA, n.d.).

\subparagraph{Ultraviolet}

UV (ultraviolet) light refers to the region of the electromagnetic spectrum between visible light and X-rays, with a wavelength 
between 400 and 10 nanometers. Among ultraviolet rays, red is the light with the longest wavelength, and violet is the light 
with the shortest wavelength. Therefore, the light with the longest wavelength is called infrared light, and the light with the 
shortest wavelength is called ultraviolet light (Stanford Solar Center, n.d.).

\subparagraph{X-ray}

X-rays are a penetrating form of high-energy electromagnetic radiation. The wavelength range of most X-rays is 10 picometers 
to 10 nanometers, the corresponding frequency range is 30 terahertz to 30 hertz (30×1015 Hz to 30×1018 Hz), and the energy range 
is 124 eV to 124 keV (Wikimedia Foundation. (2021, September 1).

\subsubsection{Spatial, spectral, and temporal resolutions in remote sensing}

\subparagraph{Spatial resolution}

In remote sensing, the spatial resolution shows the smallest possible feature that a satellite image can display, which means 
that the size of a pixel on the ground constitutes the smallest "point" of an optical satellite image. If the satellite tries 
to capture the size of the scene 700KM from the earth (300m x 300m), the imaged pixels will be very low and the image will become 
very blurry (Muhebwa, A, nd). The spatial resolution is divided into 3 levels:

Low resolution: more than 60m/pixel
Medium resolution: 10 ‒ 30m/pixel
High resolution to ultra-high resolution: 30cm ‒ 5m/pixel

Not many details about the capture are determined by the pixels of the spatial resolution. If improvements are made to obtain 
more captured details, a large number of cameras will be required to achieve detailed scenes. For the same purpose, space scientists 
need to use a single-pixel to represent the linear dimension on the ground, where the difference in pixels and colors will be 
recommended for measurements on the earth according to the satellite's use and coding method. In the 1980s, NASA satellite data from 
Landsat had 60 million pixels at the time, but with the advancement of the times and the rapid development of technology, 60 million 
pixels have become less leading. The current highest resolution satellites can provide 30 cm accurate imaging (EARTH OBSERVING SYSTEM,2021, August 2).

\subparagraph{Spectral resolution}

The International Commission on Illumination (CIE) organization defines the light response of human vision as the range of 380nm to 
780nm and provides a weight table so that the public can use the instrument to study the measured value at the wavelength multiplied 
by the corresponding human vision (Michael. (2021, June 21)). These tables are provided at intervals of 1 nanometer, 5 nanometers, 
and 10 nanometers. Resolution refers to how many data points are used in the calculation of the image. For the spectral resolution, 
it is to define the measurement point in the spectral result one step further.

\subparagraph{Temporal resolution}

Time resolution refers to the repetitive period or frequency at which the sensor revisits the same part of the earth's 
surface. Think of it as the time to take multiple measurements of the cross-section and then reconstruct the image. This 
time is also called the "revisit time" of the satellite. For example, the greater the stripe width of a polar-orbiting 
satellite, it is regarded as the width of the sensor's "cross-orbit" field of view during the passage of the orbit, and 
the higher the resolution time (Watson, N. J, 2015).

@@

\subsubsection{Data Overview}

The Resources on AWS:

\text{Description}

Light Every Night dataset of all VIIRS DNB and DMSP-OLS nighttime satellite data

\text{Resource type}

S3 Bucket

\text{Amazon Resource Name (ARN)}

arn:aws:s3:::globalnightlight

\text{AWS Region}

us-east-1

\text{AWS CLI Access (No AWS account required)}

aws s3 ls s3://globalnightlight/ --no-sign-request
For implementing the web-level application, understanding the database of the Light Every Night dataset is essential 
for our team. Then I have accessed this dataset via the AWS instance Linux server. 
Under this path, there are three main types of folders, like-named by date (201204,201505…201603), named by satellites 
(F10, F12…F18), and named by npp\_date.

\subsubsection{DMSP-OLS}

DMSP is a series of polar-orbiting satellites of the US Air Force. The sensors on this model satellite were used in the 
initial design to observe weather-related indicators in the visible and infrared wavelength ranges during the day and night. 
DMSP satellites can be divided into "day/night" or "dawn/dusk" satellites according to their transit time. One side of the 
orbit of the day and night satellite images the dayside of the earth, and the other side images the night side. In 1992, when 
the digital archive began to be created, two DMSP satellites collected data and named them F10 and F11. F10 is in day/night 
orbit, F11 is in dawn/dusk. Since then, eight satellites have been launched, F12-F19, of which F12, F14, F15, F16, and F18 
were launched in day/night orbits.

This part DMSP-OLS data which are named from DMSP satellites as I mentioned before. The file name was generated from the 
satellite's name and year. Like F101992, which means the data was collected by satellite F10 in 1992. There are many files 
from 1992 to 2013 that can be used by the public.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/2.png}}
    \caption{folders}
    \label{folders}
\end{figure}

This picture is showing lots of folders of nighttime data.  In those folders, there are tons of.OIS files. 
For example: F12199501010014.night.OIS

F12 -> satellite name \\
1995 -> year at start of orbital segment \\
01 -> month at start of orbital segment \\
01 -> day of month at start of orbital segment \\
00 -> hour of day at start of orbital segment \\
14 -> minute of hour at start of orbital segment \\
.night -> orbit is cropped to only nighttime data \\
.OIS -> acronym for OLS Interleaved Smooth \\

All those details about this file are giving more information for users to understand how the data be stored in the AWS database server.

The satellite's timeline illustrates that the "F" satellites be used in different years.

\begin{figure}[htbp]
\centerline{\includegraphics[width=260pt]{images/2.1.png}}
\caption{nighttime data}
\label{nighttimedata}
\end{figure}

The line chart demonstrates the different periods of how they are used in acquiring nighttime data.  It is clear to know F10 satellite 
is the first one which is used in collecting nighttime data in 1995. Then more and more satellites like F11, F12, F13, and F19 be created 
to take monitoring data missions.

\subsubsection{VIIRS-DNB: the follow-on sensor for the DMSP-OLS}

The follow-on sensor for the DMSP-OLS is called the VIIRS-DNB sensor, therefore there are many aspects of the VIIRS-DNB sensor that 
are the same as DMSP-OLS. Compared with DSMP-OLS, DNB is a scanning radiometer capable of low-light imaging and is launched on a sun-synchronous 
polar-orbiting platform. They regularly collect 14 orbits every day and image the earth during the day and night every 24 hours. According to 
the basic data of collection, they might look exactly the same but do more researches on nighttime data, almost all aspects of the DNB sensor 
itself are better than DSMP-OLS.

\begin{figure}[htbp]
\centerline{\includegraphics[width=260pt]{images/3.png}}
\caption{satellite}
\label{satellite1}
\end{figure}

The compared satellite pictures above show the different resolutions and details, and the result illustrates the VIIRS DNB's satellite 
data providing a clearer image.

In the AWS database, the folder includes massive files with NPP titles or names by date.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/3.1.png}}
    \caption{files}
    \label{satellite2}
\end{figure}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/3.2.png}}
    \caption{files}
    \label{satellite}
\end{figure}

The file named npp\_year and month is because of the data collection from VIIRS-DNB (the following DMSP-OLS sensor). 
It has some difference between DMSP.

For example:
SVDNB\_npp\_d20150504\_t1335358\_e1341162\_b18219\_c20150504194116381040\_noaa\_ops.rade9.co.tif

The file structure is:\\
npp\_d20150504\_t1335358\_e1341162\_b18219\\
npp:satellite ID\\
d20150504: start date of first scan in aggregate (2015/05/04)\\
t1335358: time of first scan (13:35:35.8)\\
e1341162: time of last scan (13:41:16.2)\\
b18219: orbit number of first scan\\

SVDNB\_npp\_d20150504\_t1335358\_e1341162\_b18219\_c20150504194116381040\_noaa\_ops\\
SVDNB: Day/Night Band SDR (all possible product IDs are listed below)\\
npp\_d20150504\_t1335358\_e1341162\_b18219: aggregate identifier\\
C20150504194116381040: creation date/time of SDR\\
noaa:data origin\\
ops:data domain

\subsubsection{Data structure}

The geospatial data be collected by satellites then all data will be stored in different types of formats or data types. 
In our project, there are two types of data formats, Raster file, and Vector file.

\paragraph{Raster file}

The raster image is an image file format, which is composed of a pixel matrix composed of multiple grids, and each pixel 
contains an information value. The change of this information value will be reflected in different colors, positions, and 
sizes. The most commonly used raster data, such as aerial photographs, satellite images, or elevation surfaces. These 
oversized pictures are taken and collected through the reflection of the spectrum. Moreover, today's raster images are 
usually .BMP, .GIF, .JPEG, .PNG and .TIFF files (Katie, 2020, May 8). At present, almost all the images that the public 
can see on the Internet and the images taken by digital cameras are raster images. In our project, TIFF data files will 
become our research object.

\subparagraph{Use raster as the base map}

In GIS, raster data is usually used as the background display screen of other feature layers. Such layers are orthophotos, 
which not only provide additional information but also make map users more confident that the map layers are spatially 
aligned and represent actual objects. There are three main sources of such images, namely orthophoto aerial photography, 
orthophoto satellite images, and orthophoto scanned maps (ArcGIS for Desktop, (n.d.).

\subparagraph{Use raster as a surface map}

Rasters are usually used to represent data that changes continuously along the surface, such as rainfall, temperature, 
density, etc. The map draws the surface of the map through the continuously changing data of countless small grids. The 
continuous change of grid color reflects the change of a region at present or within a period (ArcGIS for Desktop, (n.d.).

\paragraph{Vector file}

In our project, the vector format data is not the main research object, but it is also a format that our team needs 
to understand. A vector data file is an image that can be scaled to any size without losing its quality and clarity. 
Changing the file has an advantage because its scaling depends on mathematical equations. This vector file is more 
flexible and has perfect image quality. Compared with Raster files, pixilation will not lose sharpness when zooming 
in, and raster graphics will be greatly affected to form sharp contrasts (Logogenie.net,n.d.).

\subsubsection{GeoTIFFs \& Cloud-optimized geoTIFFs (COGs)}

Most of the files in the data on the AWS server are TIFF or TIF files, and these files are a file format used to 
store raster files. GeoTIFF is a TIFF file that follows specific standards used to construct metadata, such as geographic 
reference information, spatial extent, resolution, and number of layers.

Cloud Optimization GeoTIFFs (COG) is a cloud-optimized file viewing, reading, and usage solution. The OGC GeoTIFF standard 
is the OGC implementation standard (NASA, 2021, September 8). The files of GeoTIFFs are also GeoTIFF, and this data structured 
method allows users to query these files through Web services. However, this advantage allows users to query, analyze, visualize 
or download part of the COG file online without downloading the entire file. Such a database reading solution is also used by our team.

\subsubsection{Spatial-Temporal Asset Catalog (STAC) standard}

The SpatioTemporal Asset Catalog (STAC) specification provides a common language to describe a series of geospatial 
information in order to provide easier indexing and searching. A "space-time asset" is any file that represents information 
about the Earth captured in a specific space and time. The STAC specification is to allow all providers to publish new data 
sets or APIs without writing new code when they are published as a spatiotemporal asset catalog (SpatioTemporal Asset Catalog, n.d.). 
First of all, for providers, STAC is a standardized method for exposing Spatio-temporal data collections while cataloging 
assets and STAC is also a unified asset indexing method. Second, developers can build infrastructure to host, ingest, or 
manage spatial data collections, and can be extended to customize domains. Finally, data consumers often have to build a 
unique pipeline for each different data set they use.

\subsection{imagery processing in AWS}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/dataprocess.png}}
    \caption{imagery processing in AWS}
    \label{fig4}
\end{figure}
